Here we will present the two VTS collected from the literature.

\subsection{Mammalian VTS}
\input{fig-mukund-vts}

The Figure~\ref{fig:mukund-vts} represent mammalian SNARE map
created by studying the wide array of literature.
% 
To construct the map, we have assumed that vesicles only contain a
single active v-SNARE, and we have attributed t-SNAREs and inactive
v-SNAREs that travel between compartments to one of the known vesicles
that go between the same source and target compartments.
%
In order to identify the active SNARE complex involved in any
particular vesicle fusion, we used two criteria.
%
The SNARE complex is formed \textit{in vivo}. In most papers, this is
determined by immunoprecipitation of the SNARE complex from the
relevant cell fraction.
%
Blocking SNARE complex formation (for example, using antibodies
against these SNAREs, or using cytosolic forms of these SNAREs) blocks
the specific transport step.
%
Note that these vesicles have been collected from multiple cell types, and
any given cell type is likely to contain only a subset of the vesicles in
the map.

In this figure, the rectangles represent compartments, the identities
of compartments are written within ER=endoplasmic reticulum,
ERGIC=ER-Golgi intermediate compartment, RE=recycling endosome,
EE=early endosome, LE=late endosome, LYS=lysosome, PM=plasma
membrane. The arrows represent vesicle edges.


% \ashu{Adopt }
% The set of SNAREs contained in these edges are written alongside each
% edge.
% %
% Actual names of these SNAREs are mentioned in the key
% alongside.
% %
% The red labels represent the paths taken by SNARES of the
% complex Stx-4-SNAP23-VAMP7.
% %
% Here, the cycles for two SNARE molecules,
% VAMP7 and SNAP23 are complete.
% %
% The green labels represent the paths
% taken by SNAREs of the complex Stx13-SNAP25-VAMP2.
% %
% Here the cycle for
% VAMP2 is complete. The blue labels represent the paths taken by SNARES
% of the complex Stx5-Gs28-Bet1/GS15-Ykt6.
% %
% Here, cycles for none of the
% SNAREs are complete.
% %
% So, even though most edges known so far are
% present in the map, paths for molecules (SNAREs) across the cell are
% still not complete.


\subsection{Yeast VTS}

\input{fig-yeast-vts}

In Figure~\ref{fig:yeast-vts}, we present the yeast VTS.
%
We have borrowed the VTS from~\cite{burri2004complete}.
%
It has been adapted from the paper by
separating the v and the t SNAREs. 
%
It is clear that it is an incomplete description of the VTS.
%
For example, the inactive molecules were not reported in the reference.
%
We are currently searching for more literature that can help us complete
all known information about the VTS.
%


% It is important to note that it is not trivial collect all the information
% about such systems.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
