
%Motivate VTS
Eukaryotic cells, including human cells, consist of multiple membrane
bound compartments.
%
Material is transported among these compartments by the vesicle
transport system (VTS).
%
Briefly, the source compartment produces a membrane bound packet of
molecules called a vesicle.
%
After release, this vesicle specifically recognizes the correct target
compartment within the cell, and fuses with it.
%
A lot of information about the molecules that form the machinery of
the VTS has been discovered, including their regulatory interaction
with each other. 
% %
% \todo{connect to function }{We also know a lot about the specific functions} of these molecules and how these molecules interact amongst each other.
%
In spite of this detailed knowledge at the level of the molecules, the
structure of the VTS network, or the road-map of the eukaryotic cell,
is far from complete.
%
The current knowledge of the network is put together from a patch work
of biological experiments and is scattered across several publications.
%
Even after this information is collected and put together, we find
that the network obtained is still not complete; new vesicles and new
contents in previously known vesicles are constantly being discovered.
%
The synthesis for the unknown pieces may be assisted by computation on
the graph model of VTSs.
%
% 
%In this work, we use a model described in [] to find out, given a partial
%VTS graph and details about interactions amongst its molecules, what the complete graph of the
%VTS could look like. (Please look at appendix A for the detailed discussion on pros and cons of the
%model.
%
%Eukaryotic cells, including human cells, consists of multiple compartments.
%
%Vesicle Traffic Systems(VTSs) are the material transport mechanisms among the compartments inside the cells~\cite{vtsIntro}.
%
%Almost all subsystems of the cells depend on VTSs.
%
%Therefore, understanding how VTSs functions is one of the key
%questions of cell biology.
%
In this paper, we are looking at the computational questions 
arising from the VTSs.


We use the model of VTSs that has been presented in~\cite{shukla2017discovering}.
%
Please look at appendix~\ref{sec:model}
for a detailed discussion on pros and cons of the model.
% Describe VTS in detail


VTSs are regulated by the same molecules that they transport. Molecules on compartments and on vesicles can be in either an active or an inactive state.
% the term vesicle has already been introduced.. using two terms for the same object seems confusing. 
%
% (The molecules are transported to the other compartments via
%unidirectional channels.) cannot comment on unidirectionality of vesicles. they may be undergoingmultiple cycles of back-fusion for all we %know..  
%
The active molecules regulate the vesicle they occur on.
%
A vesicle is enabled by a set of molecules
such that one part of the set occurs in the vesicle and the other part
occurs in the target compartment.
% use either target or destination consistantly throughout..i prefer target because that's what the t in t-SNARE stands for.
%
These molecules must be active in the vesicle
and target compartment respectively.
%
The pairs are called {\em fusing} sets and analogously
the vesicle is considered to be {\em fused} with the
destination compartment.
%
Not all molecule sets can participate in the fusion, the
potential fusion pairs are usually determined by biological experiments.
%
Generally, in cells, the fusing pairs are found to be distinct for distinct vesicle-compartment fusions.
%
In order that a molecule that has participated in a fusion does not interfere
with fusion at compartments and vesicles, in the model, we require that the molecule is inactive on appropriate compartments.
%
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecules in a compartment or
vesicle may make the molecule active or inactive.
%
We call this regulation as {\em activity functions}.

% Defending our model
%
In this VTS model, we assume that the system is in steady state and the
concentrations of the molecules in the compartments do not change over
time.
%
We model the system as a labelled graph, where compartments are nodes and
transport vesicles are edges.
%
The set of molecules present and their activity in a compartment or
a vesicle is the label of the respective node or edge.
%
The regulation controls are defined by a fusion pairing relation
containing pairs of molecules and activity
Boolean functions.
%
Since our system is in steady state, we expect that any molecule that
leaves a compartment must come back via some path on the graph.
%
We call this property of VTS as {\em stability}.

% Partial info defence
%
As we have discussed earlier, our understanding of VTSs is partial.
%
% It largely means that the current knowledge is due to the patch work
% of biological experiments~\cite{model} for identifying the compartments,
% channels, molecules, and their activity and regulatory control.
% %
% Often the information is scattered around in several publications.
% %
% Even after with some effort we may collate all the known information about
% a VTS, we may still have unknown pieces of the system; new vesicles and new contents in previously known vesicles are constantly being discovered.
%
%{Speculative: Make a case for completing partial parts of VTSs!!}
%
%For example, it is possible that some edges may not have been
%discovered in a VTS that does not satisfy the stability condition.
% nature of missing information has already been elaborated upon in the first paragraph
%
The synthesis for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%
In this paper, we consider several versions of the synthesis problem
involving different parts of VTSs that can be synthesized, such as
modifying labels, adding/deleting edges, and learning activity functions.
%
We also consider variation on the properties against which we do
synthesis, namely stability, and $k$-connectedness that states that the VTS remains connected after removing any $k-1$ edges.
%
In order to synthesize the parts of a VTS such that it satisfies the
constraints, we encode the synthesis problem into one of satisfiability of
quantified Boolean formulas(QBFs). 
%

We have implemented the encoding in a flexible tool,
which can handle a wide range of synthesis queries.
%
We have applied our tool on several VTSs including two found-in-nature
VTSs.
%
% \input{fig-mukund-vts}
% %
% In figure~\ref{fig:mukund-vts}, we present one of the two for
% mammalian cells obtained by studying the
% literature.\footnote{Please read appendix~\ref{sec:ex-vts} for more biological details.}
% %
% The VTS has six nodes and 55 molecules.
% %
% We can easily check that stability condition is not satisfied for
% many molecules for example ???.
% %
% On the example, our synthesis tool reports that minimum ?? edges needed
% to be added to make the VTS stable.
% %
% The dashed edges are the suggested edges from our tool.
% %

Our experiments suggest that some of the synthesis problems are
solvable by modern solvers and the synthesis technology may be useful
for biological research.
%
% We have also applied our tool on various synthetic examples to
% demonstrate that our tool scale upto the graph size size nodes, which
% is the size of typical VTSs in a eukaryotic cell.

The following are the contributions of this work:
\begin{itemize}
\item We have identified an interesting application of
  the synthesis technology.
\item We have developed encoding of the synthesis problem in QBF.
\item A user friendly and scalable tool based on QBF solvers
\end{itemize}

The rest of the paper is organized as follows.
%
% In section~\ref{sec:example}, we present a motivating example.
% %
In section~\ref{sec:prelim}, we present the graph model of VTSs and encoding of several
constraints on VTSs.
%
In section~\ref{sec:encoding}, we present the synthesis problems and their
encoding into QBF satisfiability.
%
In section~\ref{sec:experiments}, we present our implementation and experimental results.
%
We discuss related work in~\ref{sec:related} and conclude in section~\ref{sec:conclusion}.



%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
